Insert title of project here

### 2022-04-05 Draft Report/Draft Project.Rmd
draft
two links
Updating draft

@@

-   Write what you're thinking about!

# Dataset Information

>>>>

-   Write what you're thinking about!
-   <https://www.thetransportpolitic.com/2022/01/24/openings-and-construction-starts-planned-for-2022/>
- <https://theintercept.com/2022/02/12/wildfires-prisons-climate-california/>
- <https://cseveren.github.io/files/racialized_difference_commuting_20220320.pdf>
<https://github.com/OpenFloodAI/Climate-Change-Datasets>
https://github.com/firstlookmedia/climate-and-punishment-data
\newpage-

@@

# Dataset Information
## Methodology
### Gather Data Sources
####EJSCREEN NC
Gathered From: 
#### National Risk Index
Gathered from: https://hazards.fema.gov/nri/data-resources North Carolina

### Clean Data Sources
Filter and pipe each to just the variables of interest: location, titles, variables 1 and 2

### Present Descriptive Statistics and Maps

###
\newpage
